---
title: "R Notebook for Data Science - Excercise 5 R and Julia"
output:
  html_document:
    df_print: paged
  pdf_document: default
authot: 'Stefan Schultz, Matrikelnummer : 190279, TH LÃƒÂ¼beck'
---

# 1. Download Rstudio & R

# 2. Use Rstudio(Posit) to create rmarkdown file

```{r setup, include=FALSE}
print("Hello World!")
```

## download package ggplot2
- Installation des Packages kann über das Menü "Tools > Install Paclages..." und Eingabe des Package-Namens mit Klick auf Install, sowie Angabe des Installationsverzeichnisses installiert werden.

## import the data("iris")
- Herunterladen des Datensets von Iris „Iris.csv“ von kaggle und Speicherung auf lokaler Festplatte.
- Laden der CSV-Datei mit der Library „readr“.
- Ausgabe der Klasse und der Spaltennamen

```{r}
# use library readr for loading csv data from file.
library(readr)

# load Iris data set from csv file
Iris <- read.csv('./input/Iris.csv')

# output class name
print(class(Iris))

# print head of Iris class (column names)
head(Iris)
```
```{r}
summary(Iris)
```


## use the ggplot for all the tasks below
- Verwendung der Libarary "ggplot2" durch Einbindung von library('ggplot2')

```{r}
library(ggplot2)
```


## make a scatter plot with x-axis: Sepal.Length and y-axis: Sepal.Width, and the species should be shown in different colors

```{r}
ggplot(data=Iris, aes(x=SepalLengthCm, y=SepalWidthCm, color=Species)) + geom_point() + theme_minimal()
```


## add regression line for the previous plot with the whole dataset (regardless of the species)

```{r}
ggplot(data=Iris, aes(x=SepalLengthCm, y=SepalWidthCm, color=Species)) + geom_point() + geom_smooth(method = lm) + theme_minimal()
```


## calculate the Pearson correlation for this plot

```{r}
# ggplot(data=Iris, aes(x=SepalLengthCm, y=SepalWidthCm, color=Species)) + geom_point() + geom_smooth(method = lm) + theme_minimal() + sm_statCorr()
```


## make the boxplot for Petal.Width with 3 species separately in the x-axis in different colors

```{r}
options(repr.plot.width = 5, repr.plot.height = 4)

ggplot(data=Iris, aes(x=Species, y=PetalWidthCm, color=Species)) + geom_boxplot() + theme_minimal() + theme(legend.position="none")
```

## make the histogram for Petal.Width with 3 species separately in x-axis in different colors

```{r}
ggplot(data=Iris,aes(x=SepalWidthCm)) + geom_histogram(binwidth=0.1) +theme_minimal()
```

## run the t-test of Petal.Width between setosa and virginica, and give the conclusion if the width is a statistically significant difference between 2 species

```{r}
# Subsets aufbauen, mit Filterung nach den Species-Bezeichnungen
Setosa <- subset(Iris, Species == "Iris-setosa")
Virginica <- subset(Iris, Species == "Iris-virginica")

# test ausführen
t.test(Setosa$PetalWidthCm, Virginica$PetalWidthCm)
```

